\section{Guava \& Cream Cheese Pop Tarts with Lime Icing}
\begin{recipe}
	\source{How To Love Cooking}
	\yield{Approximately 8 tarts, 2" $\times$ 4"}
	\cooktime{??}
	
	\pre{A twist on a Cuban classic. A brick of guava paste can be found at certain grocery stores and world food markets (such as ``World Market'').}
	
	\ingredients{
		2 				& ready-bake pie crusts \\
		1				& (half) packet of guava paste \\
		4				& oz. (\sfrac{1}{2} block) cream cheese, softened \\
		1\sfrac{1}{4}	& \t vanilla \\
		3				& \T powdered sugar \\
		1				& pinch of salt \\
		1				& egg (mixed with splash of water for egg wash)
	}
	
	Preheat oven to 400$^{\circ}$F.
	
	Prepare cream cheese filling: put cream cheese into small bowl, add powdered sugar, vanilla, pinch of salt, and mix well.
	
	Slice the guava into 8 small, thin, rectangular slices (approximately 1"$\times$2"). Roll out the pie crusts onto a cutting board, trimming the edges to make 2 squares. With a small paring knife, cut the dough into small rectangles. They should be about twice the size of the guava rectangles. Re-roll extra dough for more rectangles.
	
	On every other rectangle, place one slice of guava and about \sfrac{1}{2} to 1 Tbsp. of the cream cheese mixture. Top with another rectangle of pie dough. Seal with a fork and make a small opening in the top with the knife, for steam to escape. Brush the tops with egg wash.
	
	Bake for 12-14 minutes, until the dough is cooked through and the tarts are golden brown. Remove, and place on a rack to cool. Do not ice until mostly cooled or icing will melt into a mess.
		
	For the icing:
	
	\ingredients{
		\sfrac{1}{4}	& \cup powdered sugar \\
		\sfrac{1}{2}	& \T lime juice \\
		\sfrac{1}{2}	& \t lime zest \\
		1				& pinch of salt
	}

	Mix icing ingredients until well combined. The icing should be thick but able to drizzle. Add more lime juice or sugar until you get the desired consistency. Drizzle over the pop tarts. It's tart, so a little goes a long way!
	
	
	
\end{recipe}
