\section{Vegan Pumpkin Cookies}
\begin{recipe}
	\yield{12 cookies}
	
	\pre{These frosted cookies only use a little bit of the canned pumpkin. Use the rest to make pumpkin bread!}
	
	\ingredients{
		1				& stick (vegan) butter, softened \\
		\sfrac{1}{2}	& \cup sugar \\
		\sfrac{1}{4}	& \cup brown sugar \\
		1				& \t vanilla \\
		\sfrac{1}{4}	& \cup canned pumpkin \\
		1\sfrac{1}{2}	& \t flour \\
		1				& \t baking powder \\
		\sfrac{1}{2}	& \t baking soda \\
		\sfrac{1}{4}	& \t salt \\
		1				& \t pumpkin pie spice \\
		\sfrac{3}{4}	& \t cinnamon \\
		1				& \T (almond) milk \\
	}
	
	Add butter to large bowl and cream with mixer for 1 minute. Add sugars and vanilla and beat for 1 minute. Add pumpkin and mix 1 minute.
	
	Combine dry ingredients in separate bowl, then add to butter/sugar bowl and mix to combine. Do not overmix.
	
	Add milk and mix until soft dough forms. Refrigerate for 30 minutes minimum, overnight maximum.
	
	Preheat oven to 350$^{\circ}$F. Bake cookies on ungreased baking sheet, 10-12 minutes or until slightly golden. Cool on sheet, then rack.\\
	
	\textbf{Pumpkin frosting: }	
	
	\ingredients{
		1				& stick (vegan) butter, softened \\
		1\sfrac{1}{2}	& \T canned pumpkin \\
		\sfrac{1}{2}	& \t vanilla \\
		2\sfrac{1}{2} to 3	& \cup powdered sugar \\
		\sfrac{1}{4}	& \t cinammon \\
		\sfrac{1}{4}	& \t pumpkin pie spice \\
						& splash of almond milk \\
	}

	Beat butter until fluffy, then add vanilla, spices, pumpkin, and mix again. Add powdered sugar \sfrac{1}{2} cup at a time until thick. Drizzle enough milk to thin slightly. Frost when cool.
	
	
\end{recipe}
