\section{Homemade Thin-Crust Pizza}
\begin{recipe}
	\yieldsourcetime{Two 10" pizzas}{Blog: The Kitchn}{45-60 minutes}
	% https://www.thekitchn.com/recipe-homemade-thin-crust-pizza-recipes-from-the-kitchn-45499

	\pre{The key to a good pizza is a great crust.}


	\ingredientlist{
		\header{For the dough:}

			\sfrac{3}{4} \cup lukewarm water

			8 oz. (1 cup) cottage cheese

			\sfrac{1}{2} \cup heavy cream

			2 garlic cloves, minced

			1 \t cornstarch

			\sfrac{1}{4} \t salt

			\sfrac{1}{4} \t pepper  \newline\newline\newline\newline

			\header{For the toppings:}

			\sfrac{1}{4} \cup olive oil

			1 onion, chopped fine

			1\sfrac{1}{2} \t sugar

			\sfrac{1}{2} \t red pepper flakes

			\sfrac{1}{2} \t dried oregano

			\sfrac{1}{2} \t salt

			4 garlic cloves, minced

			28 oz. can crushed tomatoes

			14.5 oz. can diced tomatoes

			\sfrac{1}{2} \cup Pecorino Romano cheese, grated

			\sfrac{1}{4} \cup tomato paste
	}

	Arrange a rack in the bottom third of the oven, place a rimmed baking sheet on the rack, and heat to 450\degree{F}. Meanwhile, make the dough.

	Pour the water into a medium bowl. Sprinkle the yeast over the water, and let stand until the yeast is dissolved and foamy, 3 to 5 minutes.

	Add the flour and salt. Mix with a stiff spatula or wooden spoon until floury, shaggy dough forms. Turn the dough out onto a work surface and knead until it forms a smooth, slightly tacky ball that springs back when you poke it, 5 to 8 minutes. If the dough sticks to your hands like bubblegum, add a tablespoon of flour at a time until it’s easier to work with; avoid adding too much flour if possible.

	Cover the dough with the upside-down bowl or a clean kitchen towel and let sit while you prepare the pizza toppings, about 10 minutes.

	Divide the dough into 2 equal pieces. Working with one piece of dough at a time, stretch or roll it into a thin, 10- to 12-inch round. Form from the middle of the dough outwards, using the heel of your hand to gently press and stretch the dough until it's about a 1/4-inch thick or less. For an extra-thin crust, roll it with a rolling pin. If the dough starts to shrink back, let it rest for 5 minutes and then try rolling again.

	Carefully remove the preheated baking sheet from the oven and place it upside down on a wire rack. Transfer the dough directly onto the upside-down baking sheet. Brush the dough with 1 teaspoon of the oil. Spread 1/4 cup sauce into a thin layer onto dough, leaving a 1/2-inch border. Sprinkle on the cheese and other toppings.

	Bake until the crust is golden-brown and the cheese is melted and browned in spots, 8 to 12 minutes. Remove the pizza from the oven and cool for about 5 minutes before slicing and serving. Repeat with the remaining dough and toppings.



\end{recipe}
