\section{One-Hour Dinner Rolls}
\begin{recipe}
	\yield{24 rolls}
	\cooktime{60 minutes}
	\source{Blog: Inquiring Chef}
	
	\pre{...}
	
	\ingredients{
		1 \sfrac{1}{2}	& \cup warm water (110$^{\circ}$F) \\
		1				& \T instant or fast-acting yeast \\
		2				& \T granulated sugar \\
		2				& \T unsalted butter, softened \\
		4				& \cup all-purpose flour \\
		1				& \t kosher salt
	}
	
	
	For topping:
	
	\ingredients{
		3				& \T unsalted butter, melted \\
		1				& \t sea salt or kosher salt
	}
	
	
	In bowl of a stand mixer fitted with a dough hook, stir together warm water, yeast, and sugar. Let stand until creamy, about 5 minutes.
	
	Add butter, 2 cups of the flour, and salt (making sure that the salt is added on top of the flour and doesn't come in contact with the yeast until you begin mixing). Mix on low-speed until the ingredients begin to come together. Still on low-speed, add 1 cup of the remaining flour and mix for 1 minute.
	
	Add the remaining 1 cup flour. Mix on low-speed until the final addition of flour is fully incorporated into the dough. Increase the speed to medium and knead until the dough is smooth and elastic, about 5 minutes. (You will know it is ready when the dough starts to make a slapping sound as it hits the sides of the bowl.)
	
	Remove the bowl from mixer and cover with a dish towel. Let the dough rise in a warm place until doubled in volume, about 20 minutes.
	
	Turn the dough out onto a lightly floured surface and form it into an even ball. Using a serrated knife, cut the dough in half vertically, then each half vertically again into thirds so you have 6 equal strips of dough. Cut each strip of dough into fourths by cutting horizontally to make 24 little squares of dough. With lightly floured hands, roll each into a ball. Place each into a lightly greased 9×13 baking pan in rows of 4.	Cover the rolls with a dish towel and let them rise while your oven is preheating to 400$^{\circ}$F, about 20 minutes.
	
	Lightly brush the rolls with half of the melted butter (reserve the other half). Bake until golden brown, 13-15 minutes.
	
	Immediately after removing the rolls from the oven, brush them with the remaining melted butter and sprinkle with salt. Flip the pan over to remove the rolls. Serve immediately.
	
	
	
	
\end{recipe}
