\section{Soft Pretzels}
\begin{recipe}
	\yieldsourcetime{6-8 servings}{America's Test Kitchen}{75 minutes plus 1 hour rise time}

	\pre{Try with the beer-cheese soup!}

	\ingredientlist{
		\header{For the dough:}

		2 \cups bread flour

		1 \tsp instant or rapid-­rise yeast

		2 \tsp kosher salt

		1 \T packed brown sugar

		1 \T vegetable oil

		1 \sfrac{1}{2} \cup warm water (110\degree{F})

		vegetable oil spray

		\header{For boiling pretzels:}

		\sfrac{1}{4} \cup baking soda

		4 \cup water

		more pretzel salt (or kosher salt)
	}

\smallheader{For the dough:} In bowl of stand mixer, add \sfrac{3}{4} \cup warm water, 2 \T vegetable oil, 2 \tsp instant yeast, and 2 \T packed dark brown sugar.  Whisk together and let foam for 3 minutes.

In large bowl, combine flour, vegetable oil, kosher salt. Add to yest mixture, and run on the lowest spread with dough hook for about 5 minutes. Mix until no dry flour is visible, about 2 minutes.

Sprinkle flour and knead dough for about a minute, then form dough into smooth ball. Spray inside of large bowl with vegetable oil spray. Place dough in greased bowl. Cover bowl with plastic wrap and let dough rise until doubled in size, 1 hour. It should double in side. Keep the plastic wrap.

\smallheader{After rising:} cut into 6 even sections. On a cutting board with a little vegetable spray, roll into a 22" loaf, shape into a U, cross the ends at the middle twice. Then bring the ends to the bottom to make the pretzel shape. Transfer to flour-lined baking sheet, cover with plastic wrap, and let proof for 20 minutes.

Boil four cups of water and \sfrac{1}{4} \cup baking soda. Don't submerge, but boil for 30 seconds, flip, boil for 15 seconds. Place on wire rack. Drain for five minutes.

Preheat oven to 425\degree{F}. Sprinkle pretzel salt on pan, place pretzels, sprinkle salt. Bake for 15-20 minutes until mahogany.

\end{recipe}
