\section{Butter Chicken}
\begin{recipe}
	\yield{About 4 servings}
	\cooktime{5\sfrac{1}{2} hours}
	\source{Dinner then Dessert}
	\pre{This recipe is easily doubled and freezes well.}


\ingredients{
	1				& c. plain yogurt \\
	1				& T. lemon juice \\
	2				& t. ground cumin \\
	1				& t. ground cinnamon \\
	1	& t. cayenne pepper \\
	\sfrac{3}{4}	& t. black pepper \\
	1	& t. ground ginger \\
	1	& t. salt \\
	3	& boneless skinless chicken breasts
}

In a large ziploc bag, the night before cooking, add the yogurt, lemon juice, cumin, cinnamon, cayenne, black pepper, ginger, salt, and chicken (leave the chicken breasts whole). Zip the bag closed and work the mixture into the chicken until all incorporated. Refrigerate overnight.


\ingredients{
	1				& T. butter \\
	1				& clove garlic, minced \\
	1				& jalapeno, finely chopped \\
	1				& T. ground cumin \\
	1				& T. ground paprika \\
	1				& t. salt \\
	1				& 8 oz. can tomato sauce \\
	1				& c. heavy cream \\
	1				& T. cornstarch \\
	1				& T. water \\
	\sfrac{1}{4}		& c. fresh cilantro, chopped \\
	& basmati rice
}


Scrape off the majority of the marinade that is on the chicken and discard it. You'll have plenty of the second sauce to keep the food moist. Cut the chicken into two-inch chunks. Add the butter, garlic, and jalapeno into the bottom of the slow cooker. In a small bowl, add the cumin, paprika, salt, tomato sauce, and heavy cream. Stir to combine. Pour the sauce over the chicken, cover, and cook on low for 4-5 hours.

Pour the cornstarch into the water, add to slow cooker, and stir. Stir and pour quickly since you're using more cornstarch than water and it will settle quickly.

Cook an additional 20 minutes on high. Top with cilantro before serving with basmati rice.
	
\end{recipe}
