\section{Carnitas Pulled Pork}
\begin{recipe}
	\yieldtime{10-12 servings}{8 hours (slow cooker), 10 minutes (oven)}

	\pre{Hard to go wrong -- many other pulled pork recipes include diced onion, peppers, barbecue sauce, and/or cola. Pinch a little extra spice to be on the flavorful side, and consider tossing in a bay leaf so you're not a savage.}

	\ingredientlist{
		4-5 \lbs pork shoulder (bone in or out) \\
		5 cloves garlic \\
		1 \T salt \\
		1 \t cumin \\
		1 \t chili powder  \\
		1 \t  black pepper \\
		1 \t oregano \\
		\sfrac{1}{4} \t cinnamon \\
		\sfrac{1}{2} \t cayenne pepper \\
		1 \T chipotle hot sauce (opt.) \\
		2 limes, juiced \\
		\sfrac{1}{2} \cup orange juice \\
		12 \oz can standard lager beer \\
		\sfrac{1}{2} \cup salsa (less chunky) \\
		\header{Serve with:} \\
		tortillas \\
		fresh cilantro \\
		avocado \\
		limes \\
		maybe radishes or other taco things
	}

	Place the pork shoulder in the slow cooker. Roughly chop the garlic and place in the slow cooker. Sprinkle the meat with salt, cumin, chili powder, black pepper, oregano, cinnamon, and cayenne. Rub seasonings onto the pork. Add lime juice, orange juice, beer, and salsa. Cover and ideally, refrigerate overnight.

	Cook on low for 8 hours.

	Shred meat with two forks directly in the slow cooker (or take out, shred, and replace in sauce). It should fall apart easily.

	Preheat broiler. Line a baking sheet with aluminum foil. Place the shredded meat on the cooking sheet and pour a few spoonfuls of sauce over the top. Broil for 5-10 minutes or until you get browned edges on the pork.

	Serve on tortillas with fresh cilantro, avocado, and lime juice.

\end{recipe}
