\section{Tortellini, Spinach, and Chicken Soup}
\begin{recipe}
	\yieldsourcetime{About 8 servings}{Blog: 365daysofcrockpot}{10 min. prep, 3-6 hours in crockpot, 15 min. prep}

	\pre{A creamy tomato soup with cheesy tortellini and chicken and then a pop of color from the bright green spinach.}


\ingredientlist{
	1 medium yellow onion, diced

	\sfrac{1}{3} \cups all purpose flour

	1 \Tbsp dried basil

	2 cloves of garlic, minced

	2 \Tbsp tomato paste

	3 \Tbsp olive oil

	4 \cups chicken broth

	2 14.5 \oz cans petite diced tomatoes

	1 to 1\sfrac{1}{2} \lbs boneless, skinless chicken thighs

	1 \tsp salt

	\sfrac{1}{2} \tsp pepper

	4 \cups frozen cheese tortellini (or fresh)

	3 \cups packed spinach

	\sfrac{1}{2} \cup Parmesan cheese

	1 \cup heavy cream or half-and-half
}


In a microwave-safe bowl add the onions, flour, basil, garlic, tomato paste and drizzle with olive oil. Microwave for 5 minutes, stirring every 90 seconds or so. (The mixture will be pasty and look weird but don’t worry it will all be okay in the end). Add the mixture to the slow cooker*.

Add broth, tomatoes, chicken, salt and pepper to the slow cooker. Stir.

Cover and cook on LOW for 4-6 hours or on HIGH for 3-4 hours (or until chicken is very tender).

Remove the lid use a fork to remove the chicken out of the slow cooker.  And add in tortellini and spinach, Parmesan cheese and warmed cream (cream should be warmed because it may cause curdling if added in cold).

On a cutting board, shred or cut the chicken into bite-size pieces. Add the chicken back into the slow cooker. Put the lid back on and cook on HIGH for about 10 more minutes, or until the tortellini are cooked through. Ladle into serving bowls and enjoy!


\end{recipe}
