\section{Tuscan Chicken}
\begin{recipe}
	\yield{About 6-8 servings}
	
	\pre{This dish is too rich and creamy for some.}


\ingredients{
	7				& oz. jar sliced sun dried tomatoes, drained \\
	2				& T. butter \\
	4				& chicken breasts, boneless/skinless \\
	1				& small onion, diced \\
	1 \sfrac{1}{2}	& t. Italian seasoning \\
	\sfrac{1}{4}	& t. red pepper flakes \\
	15	& oz. jar Alfredo sauce (with roasted garlic) \\
	\sfrac{3}{4}		& c. Parmesan cheese (garnish) \\
	2-3				& cups fresh baby spinach
}

Drain tomatoes, set aside. Heat skillet on medium high heat and add the butter. Add chicken and brown both sides, place in slow cooker. Add onions to skillet, cook until turning translucent. Add tomatoes, cook for 2 minutes, stirring occasionally. Turn off heat, add tomatoes and onion to slow cooker. Sprinkle in Italian seasoning, red pepper flakes. Pour Alfredo sauce over the top.

Cook on low for 3-4 hours or high for 2-3 hours.

When cook time is finished, open lid and stir in Parmesan, then stir in spinach. Cook for a few more minutes, until spinach is wilted and softened. Serve over pasta or potatoes.

\ingredients{
	\sfrac{1}{2}		& c. butter \\
	1				& pint (2 c.) heavy whipping cream \\
	4				& oz. cream cheese \\
	\sfrac{1}{2}		& t. minced garlic \\
	1				& t. garlic powder \\
	1				& t. Italian seasoning\\
	\sfrac{1}{4}		& t. salt \\
	\sfrac{1}{4}		& t. pepper \\
	1				& c. grated parmesan cheese \\
}

In a medium saucepan, add butter, heavy whipping cream, and cream cheese. Cook over medium heat and whisk until melted. Add the minced garlic, garlic powder, Italian seasoning, salt, and pepper. Whisk until smooth. Add grated parmesan. Bring to a simmer and continue to cook for about 3-4 minutes, or until it starts to thicken. Toss with favorite pasta.
	
\end{recipe}
