\section{Salami and Gruyere Goug\`{e}res}
\begin{recipe}
	\yieldsourcetime{18 small goug\`{e}res}{Little French Bakery}{60 minutes}

	\pre{These small pastries go over great at parties.}

	\ingredientlist{
		\sfrac{1}{2} \cup water \\
		\sfrac{1}{2} \t salt \\
		3\sfrac{1}{2} \T butter \\
		2 \t sugar \\
		\sfrac{2}{3} \cup flour \\
		3 eggs (1 for egg wash) \\
		1 \cup gruy\`{e}re cheese, grated  \\
		\sfrac{3}{4} \cup Bolzano Old School Salami, thinly sliced then chopped
	}

	Preheat oven to 375$^{\circ}$F.

	In a small saucepan, place the water, butter, sugar and salt.  Bring to a simmer until butter melts.  Add the flour all at once, and stir.  The mixture will look like mashed potatoes.   Place the flour mixture in a mixing bowl, and add 2 eggs one at a time, stirring well after each egg.  Stir until the mixture is smooth and glossy.  Add the cheese, reserving a small amount (2-3 T), and the salami.

	Using a tablespoon or pastry bag with large tip, pipe or spoon ping pong to gold ball sized balls of dough onto a parchment lined baking sheet.  Place the last egg in a small dish and whisk with a fork to loosen.  Using a pastry brush, gently brush the top of the balls with egg.  Be careful not to drip egg on to the parchment paper from the pastry as it will keep the pastry from puffing as well as it can.  Sprinkle the tops of the puffs with extra grated cheese.

	Bake for 20-30 minutes or until completely golden brown. Cool on a wire rack and serve with mustard, pickles and more sliced salami and cheese.  Puffs can also be sliced across and filled for tiny sandwiches.

\end{recipe}
