\section{Za'atar-Spiced Beet Dip with Goat Cheese and Hazelnuts}
\begin{recipe}
	\source{Yotam Ottolenghi}
	\yield{3 cups}
	\cooktime{20 minutes preparation plus 1 hour baking beets}
	
	\pre{This bright red beet spread gets much of its flavor from za'atar, am iddle eastern spice mixture.}
	
	
	
	6 medium beets (1 1/2 pounds), trimmed 2 small garlic cloves, minced 1 small red chile, seeded and minced 1 cup plain Greek yogurt 3 tablespoons extra-virgin olive oil 1 1/2 tablespoons pure maple syrup 1 tablespoon za’atar Salt 1/4 cup roasted skinned hazelnuts, chopped 2 tablespoons goat cheese, crumbled 2 scallions, thinly sliced Warm bread, for serving 
	
	
	
	\ingredients{
		6				& medium beets (1 \sfrac{1}{2} lbs.), trimmed \\
		2				& cloves garlic, small, minced \\
		1				& red chile, small, seeded and minced \\
		1				& \cups plain Greek yogurt \\
		3				& \T olive oil \\
		1 \sfrac{1}{2}	& \T pure maple syrup \\
		1				& \T za'atar  \\
						& salt, to taste  \\
		\sfrac{1}{4}	& \cups hazelnuts, roasted, skinned, chopped  \\
		2				& \T goat cheese, crumbled  \\
		2				& scallions, thinly sliced  \\
						& warm bread, for serving
	}
	
	Preheat oven to 350$^{\circ}$F. 
	
	Put the beets in a small roasting pan and add 1/4 cup of water. Cover with foil and bake for about 1 hour, until tender. Let cool slightly.

	Peel the beets, cut into wedges and transfer to a food processor. Add the garlic, chile and yogurt and pulse until blended. Add the olive oil, maple syrup and za’atar and puree. Season with salt. Scrape into a wide, shallow bowl. Scatter the hazelnuts, goat cheese and scallions on top and serve with bread

	
\end{recipe}
