\section{Bombay Breakfast Potatoes}
\begin{recipe}
	\yield{2 to 4 servings}
	\cooktime{15 minutes prep / 25 minutes cooking / overnight chill optimal}
	\source{Blog: Food Wishes}
	
	\pre{Preparing these potatoes a night in advance simplifies morning preparation and improves their texture.}
	
	\ingredients{
		2				& large russet potatoes \\
		2				& \t ground cumin \\
		2				& \t ground coriander \\
		2				& \t turmeric \\
		1				& \t cayenne \\
		1				& \T olive oil \\
		2				& \T butter \\
		\sfrac{1}{2}	& \cup green onions  \\
		\sfrac{1}{4}	& \cup hot and/or sweet peppers, diced  \\
		\sfrac{1}{4}	& \cup cilantro, chopped \\
						& salt, to taste	
	}
	
	
	
	
	Combine cumin, coriander, turmeric, and cayenne together in small bowl. Mix well.
	
	Skin russet potatoes, cut in half, then into quarters, eighths, and sixteenths.
	
	Bring a large pot of well-salted water to a boil over medium-high heat. Add potatoes and \sfrac{2}{3} of the spice mixture and continue to boil until just tender and fairly easily pierced with a knife, about 10 minutes. Drain; transfer to a plate and let cool to room temperature, about 30 minutes.
	
	Wrap potatoes in plastic and refrigerate until thoroughly chilled, 8 hours to overnight.
	
	Remove potatoes from the refrigerator and cut in half once more (optional).
	
	Heat butter and olive oil in a nonstick skillet over medium to medium-high heat. Add potatoes and season with salt. Cook until crisped, 3 to 5 minutes. Toss with a spatula and continue to cook until golden brown, 3 to 5 minutes more. Sprinkle with remaining spice mixture, green onions, and chili peppers. Cook until onions and peppers just start to soften, 3 to 4 minutes.
	
	Transfer potatoes to a plate and top with cilantro.
		
\end{recipe}
