\section{Beer Cheese Soup Version 2}
\begin{recipe}
	\yieldsourcetime{6 cups}{The Cozy Cook}{15 min. prep, 60 min. cooking}
	% https://thecozycook.com/beer-cheese-soup/

	\pre{This simple beer cheese soup recipe can be made with a variety of cheeses and any kind of beer from Guinness to Bud Light! Caramelized onions in the broth add great depth of flavor, along with crispy bacon and green onions to garnish!}

	\ingredientlist{
		6 slices bacon

		2 \T salted butter

		1 large sweet onion, can sub yellow

		3 cloves garlic, minced

		\sfrac{1}{4} \cups flour

		12 \oz beer, see notes

		2 \cups chicken broth

		2 \cups half and half, or heavy cream

		1 \tsp mustard powder

		\sfrac{1}{8} teaspoon cayenne pepper, just a pinch

		1 sprig fresh thyme, can sub 1 \tsp dry thyme

		1 bay leaf

		3 \cups shredded cheddar cheese, see notes

		2 green onions, diced
	}


Shred the cheese from a block, measure out the half and half. Let them sit out at room temperature.

Cut the bacon into 1" squares with kitchen shears. Cook in a large pot over medium-low heat, rotating occasionally. Remove and set aside once crisp. Leave 2 Tablespoons of drippings in the pot and add 2 Tablespoons of butter.

Slice the onion into squares about \sfrac{3}{4} of an inch thick, thicker than you normally would for soup. We’re going to caramelize them down and they’ll shrink down in size. If they’re diced too small they will burn.

Heat the onions in the pot over medium low heat. Use a silicone spatula to stir occasionally and ‘clean’ the bottom of the pot. Add a small splash of olive oil if needed. Continue cooking the onions for about 25 minutes, allowing them to foam and reach a deep golden-brown color. This adds a ton of flavor to the soup.

Add the garlic and cook for 1 more minute.

Add the flour and toss to coat. Cook for 1 full minute, until you can no longer smell flour.

Add the beer. Bring to a boil, reduce to a simmer and let it bubble gently and reduce for 15 minutes. Stir occasionally.

Add the chicken broth and use a silicone spatula to clean the bottom of the pot again.

Add the half and half, mustard powder, cayenne, thyme, and bay leaf. Bring to a boil, reduce to a simmer.

Let the soup simmer until ready to serve, (at least 10-15 minutes). Remove the bay leaf and thyme stem.

Remove from the heat and let it come down in temperature for a minute. Gradually sprinkle in the cheese and stir to combine (if the soup is too hot the dairy will separate and the soup will be grainy).

Garnish with bacon and green onions and serve with crusty bread or garlic bread with cheese!
\end{recipe}
