\section{Beer Cheese Soup}
\begin{recipe}
	\yieldsourcetime{8 servings}{SAVVYHOSTESS on allrecipes.com}{30 min. prep, 45 min. cooking}
	% https://www.allrecipes.com/recipe/86274/wisconsin-natives-beer-cheese-soup/

	\pre{Try this wonderful, hearty soup with fresh bread or sourdough pretzels. Ingredients like dry mustard
	and hot pepper sauce can be substituted pretty readily. A brown or amber ale is optimal; avoid the hops of
	an IPA and the heavy flavors/colors of a stout.}

	\ingredientlist{
		1\sfrac{1}{2} \cup diced carrots

		1\sfrac{1}{2} \cup diced onion

		1\sfrac{1}{2} \cup diced celery

		2 cloves garlic, minced

		1 \tsp hot pepper sauce

		\sfrac{1}{8} \tsp cayenne pepper

		\sfrac{1}{2} \tsp salt

		\sfrac{1}{4} \tsp black pepper

		3 \cup chicken broth

		2 \cup beer (16 oz.)

		\sfrac{1}{3} \cup butter

		\sfrac{1}{3} \cup flour

		4 \cup milk or half-and-half

		6 \cup shredded sharp Cheddar cheese

		1 \T Dijon mustard

		2 \tsp Worcestershire sauce

		1 \t dry mustard

		2 \cup popped popcorn, for garnish
	}



In a large saucepan over medium heat, stir together carrots, onion, celery, and garlic. Stir in hot pepper sauce, cayenne pepper, salt, and pepper. Pour in chicken broth and beer; simmer until vegetables are tender, about 12 minutes. Remove from heat.

Meanwhile, heat butter in a large soup pot over medium-high heat. Stir in flour with a wire whisk; cook, stirring until the flour is light brown, about 3 or 4 minutes. Gradually stir in milk, whisking to prevent scorching, until thickened. Remove from heat, and gradually stir in cheese. Keep warm.

Stir beer mixture into cheese mixture. Stir in Dijon mustard, Worcestershire sauce, and dry mustard. Adjust for hot pepper sauce. Bring to a simmer, and cook 10 minutes. Serve topped with popcorn and next to fresh sourdough pretzels.

\end{recipe}
