\section{Cauliflower Turmeric Soup}
\begin{recipe}
	\yield{4 to 6 servings}
	\cooktime{15 min. prep \& 15 min. cook}
	\source{Blog: A Cozy Kitchen}
	% https://www.acozykitchen.com/cauliflower-turmeric-soup
	
	\pre{...}
	
	\ingredients{
		1				& head of cauliflower, cut into florets \\
		1				& \T olive oil \\
		\sfrac{1}{4}	& of a red onion \\
		2				& cloves garlic, still in skins \\
		2\sfrac{1}{2}	& \cup chicken broth, divided \\
		1\sfrac{1}{4}	& \cup light coconut milk (optional: more as garnish) \\
		\sfrac{1}{4}	& \t ground coriander \\
		\sfrac{1}{4}	& \t ground ginger \\
		1				& \t salt \\
		\sfrac{1}{2}	& \t fresh ground pepper \\
		2				& \t dried turmeric (or 1 \t fresh grated) \\
		1				& lime, juiced \\
						& cilantro, as garnish \\
						& sliced green onions, as garnish \\
		\sfrac{1}{4}	& \cup cliced almonds, lightly toasted, as garnish
	}
	
    Preheat oven to 400$^{\circ}$ F.
    
    On a parchment-lined baking sheet, toss together the cauliflower, red onion and garlic cloves with the olive oil. Transfer to the oven to roast for 30 minutes to 35 minutes, until the cauliflower has softened and browned, slightly. Carefully push the garlic out of its shell (it will be super soft). To a blender, add 1 \sfrac{1}{2} cups chicken broth, cauliflower, red onion and garlic. Blend until very smooth, about 2 to 3 minutes, scraping the sides as needed. 

	Pour the cauliflower mixture in a medium pot and add the coconut milk and the remaining 1 cup of chicken broth. Turn the heat to medium and stir, bringing the soup to a simmer. Add the coriander, ginger, salt, pepper and turmeric. Allow to simmer on medium-low for about 10 minutes, until all the flavors merry. Give it one last taste and adjust the salt according to your liking. Stir in the lime juice and then divide amongst bowls. 
	
	Garnish with a drizzle of coconut milk, cilantro, green onions and sliced almonds. This soup is awesome to make at the beginning of the week and then heat up whenever you like. Stays good in the fridge for up to 5 days.
	
\end{recipe}
