\section{Sp\"{a}tzle}
\begin{recipe}
	\yieldsourcetime{6-8 servings}{America's Test Kitchen}{20-25 minutes}
	% https://www.cookingsignature.com/2019/07/how-to-make-buttered-spaetzle.html

	\pre{This simple beer cheese soup recipe can be made with a variety of cheeses and any kind of beer from Guinness to Bud Light! Caramelized onions in the broth add great depth of flavor, along with crispy bacon and green onions to garnish!}

	\ingredientlist{
		2 \cups all purpose flour

		salt and pepper

		\sfrac{1}{4} \tsp ground nutmeg

		\sfrac{3}{4} \cups whole milk

		3 large eggs

		2 \T vegetable oil

		1 shallot, minced

		2 \T unsalted butter
	}

Combine flour, \sfrac{3}{4} teaspoon salt, \sfrac{1}{2} teaspoon pepper, and nutmeg in large bowl, whisk milk and eggs until combined in bowl. Slowly whisk milk mixture into flour mixture until smooth. Cover and let rest for 15 to 30 minutes.

Bring 4 quarts water to boil in Dutch oven. Add 1 tablespoon salt and set  sp\"{a}tzle maker on Dutch oven. Transfer half of batter to  sp\"{a}tzle maker and use spatula to scrape batter across holes, letting it fall into water boil until sp\"atzle float, about 1 minute. Using slotted spoon, transfer sp\"atzle to paper towel lined baking sheet to drain. Repeat with remaining batter. Pat sp\"atzle dry with paper towels. Sp\"atzle could be tossed with 1 tablespoon vegetable oil and refrigerated for up to 1 day.

Heat oil in 12" nonstick skillet over medium high heat until shimmering. Stir in shallot and cook until softened, about 2 minutes. Add sp\"atzle and cook, stirring occasionally, until golden crisp at edges, 5 to 7 minutes. Off heat, stir in butter. Season with salt and pepper and serve

\end{recipe}
