\section{``Hotdish'' Tater Tot Casserole}
\begin{recipe}
	\yieldsourcetime{2 casserole dishes (1 frozen), 5 servings each}{Blog: Taste of Home}{25 min. prep, 45 min. bake}
	% https://www.tasteofhome.com/recipes/tater-tot-casseroles/

	\pre{Although it doesn't photograph well, this comforting casserole has a pleasant spice kick.}


	\ingredientlist{
		\sfrac{3}{4} \lb bulk hot Italian sausage \\
		\sfrac{3}{4} \lb lean ground beef (90\%) \\
		1 small onion, chopped \\
		2 cans (10\sfrac{1}{2} \oz each) cream of potato soup \\
		2 \cups frozen peas \\
		1 can (15\sfrac{1}{4} \oz) whole kernel corn, drained\\
		2 \cups shredded Colby-Montery Jack cheese \\
		\sfrac{1}{2} \cup 2\% milk \\
		1 \tsp garlic powder \\
		\sfrac{1}{4} \tsp seasoned salt \\
		\sfrac{1}{4}-\sfrac{1}{2} \tsp cayenne \\
		1 package (32 \oz) frozen tater tots
	}


    In a Dutch oven, cook the sausage, beef and onion over medium heat until meat is no longer pink; drain. Add the soup, beans, corn, 1 cup cheese, milk, garlic powder, seasoned salt and cayenne. Transfer to 2 greased 11x7-in. baking dishes. Top with Tater Tots; sprinkle with remaining cheese.

	Cover and freeze 1 casserole for up to 3 months. Cover and bake the remaining casserole at 350° for 40 minutes. Uncover and bake until bubbly, 5-10 minutes longer.

	\textbf{To use frozen casserole}: Thaw in the refrigerator overnight. Remove from the refrigerator 30 minutes before baking.	Cover and bake at 350° for 50 minutes. Uncover and bake until bubbly, 5-10 minutes longer.


\end{recipe}
