\section{Cheese and Tomato Lasagna}
\begin{recipe}
	\yieldsourcetime{8 servings}{America's Test Kitchen}{2+ hours}

	\pre{Do not substitute thin no-boil noodles.}


	\ingredientlist{
		\header{Cheese sauce:} \\
		4 oz. (2 cup) Pecorino Romano cheese, grated \\
		8 oz. (1 cup) cottage cheese \\
		\sfrac{1}{2} \cup heavy cream \\
		2 garlic cloves, minced \\
		1 \t cornstarch \\
		\sfrac{1}{4} \t salt \\
		\sfrac{1}{4} \t pepper \\
		\header{Tomato sauce:} \\
		\sfrac{1}{4} \cup olive oil \\
		1 onion, chopped fine \\
		1\sfrac{1}{2} \t sugar \\
		\sfrac{1}{2} \t red pepper flakes \\
		\sfrac{1}{2} \t dried oregano \\
		\sfrac{1}{2} \t salt \\
		4 garlic cloves, minced \\
		28 oz. can crushed tomatoes \\
		14.5 oz. can diced tomatoes \\
		1 oz. (\sfrac{1}{2} cup) Pecorino Romano cheese, grated \\
		\sfrac{1}{4} \cup tomato paste \\
		\header{Lasagna:} \\
		14 curly-edged lasagna noodles \\
		8 oz. (2 cups) fontina cheese, shredded \\
		\sfrac{1}{8} \t cornstarch \\
		\sfrac{1}{4} \cup Pecorino Romano cheese, grated \\
		3 \T fresh basil, chopped
	}

	Whisk all ingredients in bowl until homogeneous. Set aside.

	Heat oil in large saucepan over medium heat. Add onion, sugar, pepper flakes, oregano, and salt. Cook, stirring frequently, until onions are softened, about 10 minutes. Add garlic and cook until fragrant, about 2 minutes. Stir in crushed tomatoes, diced tomatoes, Pecorino, and tomato paste. Bring to simmer. Reduce heat to medium-low and simmer until slightly thickened, about 20 minutes.

	While sauce simmers, lay noodles in 9"$\times$13" baking dish and cover with boiling water. Let noodles soak until pliable, about 15 minutes, separating noodles with tip of knife to prevent sticking. Pour off water and run cold water over noodles. Pat dry noodles with clean towel; dry dish. Cut two noodles in half crosswise.

	Adjust oven rack to middle and heat oven to 375$^{\circ}$F. Spread 1\sfrac{1}{2} cups tomato sauce in bottom of dish. Lay 3 noodles lengthwise in dish with ends touching 1 short side, leaving space on opposite short side. Lay 1 half noodle crosswise in empty space to create even layer of noodles. Spread half of cheese sauce over noodles, followed by \sfrac{1}{2} cup fontina. Repeat layering of noodles, alternating which short side gets half noodle (alternating sides will prevent lasagna from buckling). Spread 1\sfrac{1}{2} cups tomato sauce over second layer of noodles, followed by \sfrac{1}{2} cup fontina. Create third layer using 3\sfrac{1}{2} noodles (reversing arrangement again), remaining cheese sauce, and \sfrac{1}{2} cup fontina.

	Lay remaining 3\sfrac{1}{2} noodles over cheese sauce. Spread remaining tomato sauce over noodles. Toss remaining \sfrac{1}{2} cup foninta with cornstarch, then sprinkle over tomato sauce, followed by Pecorino.

	Spray sheet of aluminum foil with vegetable oil spray and cover lasagna. Bake for 35 minutes. Remove lasagna from oven and increase oven temperature to 500$^{\circ}$F.

	Remove foil from lasagna, return to oven, and continue to bake until top is lightly browned, 10 to 15 minutes longer. Let lasagna cool for 20 minutes. Sprinkle with basil, cut into pieces, and serve.



\end{recipe}
