\section[Pork Scaloppine with Citrus Balsamic Sauce]{Pork Tenderloin Scaloppine with Citrus Balsamic Sauce}
\begin{recipe}
	\yieldsourcetime{...}{Mom}{...}

	\pre{These scaloppine are cut thinner than medallions and cook very quickly, so do not walk away after you put them in the pan.}

	\ingredientlist{
		\header{Tenderloins:} \\
		1 lb. pork tenderloin \\
		salt, ground black pepper \\
		1\sfrac{1}{2} \t butter \\
		1\sfrac{1}{2} \t olive oil \\\newline\newline\newline
		\header{Sauce:} \\
		3-4 T. minced scallions or shallots \\
		1 T. honey \\
		pinch ground allspice \\
		1 c. chicken stock \\
		1 T. strained fresh lemon juice \\
		\sfrac{1}{4} c. heavy cream \\
		1 T. balsamic vinegar
	}

	Cut crosswise into \sfrac{1}{2}-inch thick slices. Pound them to a little less than \sfrac{1}{4} inch thick. Pat dry. Season to taste with salt and pepper.

	Heat butter and oil in a large skillet over high heat. Cook the scaloppine in batches for 30 to 60 seconds each side. They will be well browned on the outside and moist and slightly pink in the center. Remove the scaloppine to a warmed platter.

	Place the skillet over medium-high heat and add scallions or shallots, honey, and allspice. Cook, stirring, until the scallions or shallots are soft, 1 to 2 minutes.

	Increase the heat to high and add chicken stock and lemon juice. Boil, scraping up the browned bits from the bottom of the skillet with a wooden spoon, until reduced by half. Add and boil until the sauce thickens slightly, about 1 minute.

	Add heavy cream and boil until the sauce thickens slightly, about 1 minute.

	Add balsamic vinegar and salt and pepper to taste. Return the sauce to a boil, then spoon over the pork and serve immediately.


\end{recipe}
